### 2015-11-06 CVPR16/Source/applications.tex

For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
\begin{multline}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  \\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of point $\trackp{t}$ with the object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

@@

\subsubsection{Metropolis Hastings Inference}
We use Metropolis Hastings' methods \cite{mackay1998introduction} for graphical model inference. Since we are
optimizing over continuous random variables, we use Gaussian distribution as
the proposal distribution. We choose Metropolis Hastings inference over
block-coordinate descent which turns out to be slower than Metropolis Hastings
in our experiments. Please refer to the supplementary material for the
comparison of inference methods.

>>>>

For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
\begin{multline}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  \\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $N$ and $M$ are respectively the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with the object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

@@

\subsubsection{Inference on graphical model}
We apply Metropolis Hastings' method~\cite{mackay1998introduction} for performing inference on graphical model. Since we are
optimizing over continuous variables, we use Gaussian distribution as
the proposal function. We choose Metropolis Hastings over
Blocked Coordinate Descent which turns out to be slower than Metropolis Hastings
in our experiments. Please refer to the supplementary material for our comparisons of inference methods.

### 2015-11-06 CVPR16/Source/intro.tex
changes
Squeezed plots fig 3 and fig 4.

A key advantage afforded by our occlusion model is unification. While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios. In this paper, we show that our theory can be used for uniformly modeling the association of SFM point tracks with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}). We demonstrate application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.

@@

To summarize, our main contributions are:
\vspace{-0.2cm}
\begin{tight_itemize}
%\setlength\itemsep{0cm}
\item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
\item Unified occlusion handling in various applications, such as 3D points in SFM and bounding boxes in object detection.
\item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
\item Application of our unified formulation to 3D localization of traffic participants in road scenes.
\end{tight_itemize}

>>>>

A key advantage afforded by our occlusion model is unification. While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios. In this paper, we show that our theory can be used for uniformly modeling the association of SFM point tracks with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}). We demonstrate the application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.

@@

To summarize, our main contributions are:
\vspace{-0.2cm}
\begin{tight_itemize}
%\setlength\itemsep{0cm}
\item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
\item Unified occlusion handling for point tracks in SFM and bounding boxes and detection scores in object detection.
\item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
\item Application of our unified formulation to 3D localization of traffic participants in road scenes.
\end{tight_itemize}
